Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-01-14 grove-paper.tex
Add more CRDT notes to paper

@@

Logoot : a Scalable Optimistic Replication Algorithm for Collaborative Editing on P2P Networks
  \url{}

@@

@@

Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]
  http://dx.doi.org/10.1007/978-3-319-73721-8_17
  https://pages.lip6.fr/Marc.Shapiro/papers/VMCAI-2018-filesys.pdf

@@

Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]
  http://dx.doi.org/10.1007/978-3-642-16934-2_37
  http://arxiv.org/abs/1010.3615

>>>>

List of CRTD papers: \url{https://crdt.tech/papers.html}

@@

Logoot : a Scalable Optimistic Replication Algorithm for Collaborative Editing on P2P Networks
  \url{http://pagesperso.lina.univ-nantes.fr/~molli-p/pmwiki/uploads/Main/weiss09.pdf}

@@

LSEQ: an Adaptive Structure for Sequences in Distributed Collaborative Editing,
  \url{https://hal.archives-ouvertes.fr/file/index/docid/921633/filename/fp025-nedelec.pdf}

Data consistency for P2P collaborative editing
  \url{https://hal.archives-ouvertes.fr/file/index/docid/108523/filename/OsterCSCW06.pdf}

Interleaving anomalies in collaborative text editors
  \url{https://martin.kleppmann.com/papers/interleaving-papoc19.pdf}

Moving Elements in List CRDTs
  \url{https://martin.kleppmann.com/papers/list-move-papoc20.pdf}

A highly-available move operation for replicated trees and distributed filesystems
  \url{https://martin.kleppmann.com/papers/move-op.pdf}

@@

Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]
  \url{http://dx.doi.org/10.1007/978-3-319-73721-8_17}
  https://pages.lip6.fr/Marc.Shapiro/papers/VMCAI-2018-filesys.pdf

@@

Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]
  \url{http://dx.doi.org/10.1007/978-3-642-16934-2_37}
  http://arxiv.org/abs/1010.3615
